%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	Electrical Engineering resume based on Resume Document Template (Michael DeCorte)
%	Author: Jesse Wigfield
%
%	Last Modified: Oct 4, 2016
%
% Dependency: res.cls - author: (Michael DeCorte)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin,line]{res}
\usepackage{hyperref}
\usepackage{url}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\topmargin=0in
\topskip=0in
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\tab}[1]{\hspace{.2\textwidth}\rlap{#1}}
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


    
\begin{document}
\name {
\LARGE Jesse A. Wigfield \begin{normalsize}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 
\ \ \ \
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \
\ \ \ \ \ \ 
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \\
1584 Loranne Ave, Pomona, CA 91767
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 
jawigfield@cpp.edu 
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 
(760) 793-9072 
\end{normalsize}
}

\begin{resume}
%\section{\sc Contact }
%\vspace{.05in}
%\begin{tabular}{@{}p{3.5in}p{3in}}
%1584 Loranne Ave. Pomona, CA, 91767       & {E-mail:}  jawigfield@cpp.edu\\
%\end{tabular}

%\section{\sc Interests}
%Software Development involving Embedded Systems and Control Systems 

\section{\sc Education}
{\bf California Sate Polytechnic University}, Pomona, CA.  \hfill Graduating: December 10, 2016\\
%\vspace*{-.1in}
B.S. in Electrical Engineering 
%\hfill(Overall GPA: 3.55/4.0) (Core GPA: 3.94/4.0)
\hfill Core GPA: 3.94/4.0
\section{\sc Technical Skills}
{\bf Software}:  C++, MATLAB, Python, Verilog, VHDL, P-Spice, SQL, SVN, Git, LabVIEW\\
%{\bf Operating Systems}: Windows, Linux, Mac OSX\\
{\bf Hardware}: PCB Design, Microcontrollers, Spartan 3 FPGA, Motors, Oscilloscopes, Soldiering


\section{\sc Professional Experience}
{\bf NASA Jet Propulsion Laboratory}, Pasadena, CA.  \hfill{June 2016 -- Present}\\
{\em Simulation and Support Equipment Division - Intern}
\begin{list2} %Job Description%
\item Working with experienced engineers, learning the fundamentals of spacecraft simulation \& testing
\item Delivering prototype support equipment for Insight and M2020 under strict mission time-lines 
\item Adapting to variable design constraints while striving for the most robust design possible
\end{list2}


{\bf Campfire Alaska}, Anchorage, AK. \hfill{June 2015 - Aug. 2015}\\
$\bullet$ Led a team of three youth counselors to remote Alaskan communities \\
%\item Organized and executed community events with 100+ attendees 
$\bullet$ Taught the children swimming skills, cold water safety, and life skills 



{\bf China Lake Child and Youth Programs}, Ridgecrest, CA. \hfill{May 2009 - Sep. 2014}\\
$\bullet$ Directed a staff of 10-20 counselors in youth development programs \\
$\bullet$ Created three new youth clubs: Rock Wall Club, Paintball Club, and Fix-It Club

%%%%%%
%{\em Second Job Name}\hfill {August 2009 -- January 2010}\\
%\begin{list2} %Job Description%
%\item Responsible for XYZ \\
%\item Responsible for ABC\\
%\end{list2}
%%%%%%%%%%%
%%%%%%%%%%%%%%%%

\section{\sc Projects}
{\bf NASA - Electronic Support Equipment for M2020 motors} \hfill{Aug 2016 - Oct. 2016}\\
$\bullet$ Engineered hardware and user interfaces to control and protect flight hardware during testing \\
$\bullet$ Drew PCB designs and schematics for review and assembly of equipment \\
$\bullet$ Completed a design that passes the Failure Modes \& Effects Analysis, ahead of schedule

{\bf NASA - Spacecraft Simulation Auto-Coder}
\hfill{May 2016 - Aug. 2016}\\
$\bullet$ Developed Python algorithms to Query SysML spacecraft models for components \\
$\bullet$ Coordinated algorithms for component matching utilizing an SQL database of JPL components \\
$\bullet$ Auto-coded simulation initialization with matched components and their interconnections 

{\bf IEEE - Micromouse Autonomous Maze Solving Robot}
\hfill{Sep. 2105 - May 2016}\\
$\bullet$ Designed and tuned a PID control algorithm using C++ and an Atmel microcontroller \\
$\bullet$ Provided precise control of two synchronized DC motors \\
$\bullet$ Taught embedded programming in C++ to new members of IEEE


{\bf Senior Capstone - RF Range Finding}
\hfill{Sep. 2105 - May 2016}\\
$\bullet$ Implemented Silicone Instruments RF transmitters and receivers to determine distances \\
$\bullet$ Utilized PIC microcontrollers, oscilloscope FFT, and band pass filters 
%$\bullet$ Accurately measured the time of signal travel using a Texas Instruments time to digital converter \\


{\bf Spartan 3 FPGA - VHDL Trigonometric Calculator }
\hfill{Feb 2016 - Apr. 2016}\\
$\bullet$ Designed a sine and cosine calculator using the CORDIC algorithm \\
$\bullet$ Accomplished multiplication and division with structural arrays of adders

{\bf Artificial Intelligence Methods - R\&D}
\hfill{Sep 2015 - Dec 2015}\\
$\bullet$ Used MATLAB to study the effectiveness and utilization of the A* graph traversal algorithm \\
$\bullet$ Completed an algorithm that can solve mazes and illustrate the fastest possible solution

\section{\sc Personal Achievements}
{\bf Boy Scouts of America - Eagle Scout}
\hfill{Feb. 2002 - Jan. 2009}\\
$\bullet$ Orchestrated troop meetings, camp-outs, hikes, and community service events for troop 848


\end{resume}
\end{document}




